Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-29 papers/LREC2020/background.tex
a bit of shortening to fit in 8 pages

The purely taxonomic view on naming has also been criticized in more recent work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}. 
This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the main parameter that accounts for variation in our data.

@@

In Computer Vision, object recognition is typically modeled as a classification task where state-of-the-art systems localize and categorize objects according to a given labeling scheme which can comprise thousands of different categories  \cite{googlenet,ILSVRC15}. 
Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology where automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
Thus, even though object recognition benchmarks do provide images of objects and categories, they generally do not provide what we are interested in in this work, namely natural names of objects.

@@

In contrast to work on object recognition, work in L\&V typically collects and uses data sets where annotators produce free and natural utterances for a given image. 
Moreover, these data sets typically record utterances that are more complex than a single word, such as image captions \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, visual dialogues \cite{das2017visual,vries2017guesswhat} or image paragraphs \cite{krause2017hierarchical}. While object names occur in all of these data sets, they are not necessarily marked up and linked to the corresponding image regions. The overview in Section \ref{sec:survey} will discuss corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.

Our new collection, ManyNames, focuses on object names in isolation and is, therefore, substantially more controlled than typical data sets that are currently in use in L\&V. This controlled collection procedure allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.

>>>>

The purely taxonomic view on naming has also been criticized in work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}. 
This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the most frequent source of variation in our data.

@@

In Computer Vision, object recognition is often modeled as a classification task where state-of-the-art systems localize and classify objects into thousands of different categories  \cite{googlenet,ILSVRC15}. 
Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology where automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
Thus, even though object recognition benchmarks do provide images of objects and categories, they generally do not provide what we are interested in in this work, namely natural names of objects.

@@

Previous work in L\&V has collected and used data sets where annotators produced free and natural utterances for a given image. 
Moreover, these data sets typically record utterances that are more complex than a single word, such as image captions \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, visual dialogues \cite{das2017visual,vries2017guesswhat} or image paragraphs \cite{krause2017hierarchical}. While object names occur in all of these data sets, they are not necessarily marked up and linked to the corresponding image regions. The overview in Section \ref{sec:survey} will discuss corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.

Our new collection, ManyNames, focusses on object names in isolation and is substantially more controlled than common L\&V data sets. This controlled collection procedure allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.

### 2019-11-29 papers/LREC2020/conclusion.tex
a bit of shortening to fit in 8 pages

For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object categorization and naming.
Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box. 
Our data suggests that this is not always the case and provides empirical data to, for instance, assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case) or really off.
% (as in the case where they label objects as the background, like \word{grass} for \word{dog}).

>>>>

For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object categorization and naming.
Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box. 
Our data suggests that this is not always the case and can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case) or really off.
% (as in the case where they label objects as the background, like \word{grass} for \word{dog}).

### 2019-11-29 papers/LREC2020/survey.tex
a bit of shortening to fit in 8 pages

Both \refcoco and \refcocop \cite{Yu2016} use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
The matcher must click on the object she thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use location words, urging them to refer to the appearance of objects.
 % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

The statistics in Table \ref{tab:compare} suggest that the multiple annotations ($2.84$\ on average) actually contain a considerable amount of variation in naming (almost 2 different names on average per object). However, the small number of annotations per object would not allow for a reliable assessment of speaker agreement.

RefCOCO has been used to model and examine the effect of context on referring expression generation in general \cite{Yu2016}, though this work did not look at object names specifically. 
A controlled analysis of the effect of context on choice in object naming, as for instance in \cite{graf2016animal}, would require substantial further data annotation as not all objects of an image are annotated with REs and corresponding categories. Hence, so-called distractor objects  \cite{krahmer:2012} and their names cannot be analyzed systematically.
Also, while in \refcoco the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
To sum up, \refcoco is suitable for generally modeling referring expressions in context for a restricted set of categories, but less appropriate for analyzing object naming in particular.

@@

While some existing resources do provide naming data for objects in context, they do not provide \textit{enough} data to systematically assess how variable or stable object naming really is. The RefCOCO data (and to some extent the Flickr30k entities data) suggests that for most objects there is more than none available name, but it is unclear which name most speakers would prefer or whether there is such a preferred name at all. 
The VG data, to the contrary, seems to indicate that the vast majority of objects should only be associated with a single name, but it is difficult to estimate to what extent this finding results from problems with annotation (partial linking).
This shows that to be able to analyze object naming in more detail, we simply need naming data from many subjects for the same objects. 
Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
These are the motivations for our dataset, ManyNames, and for building it on top of \vg, as discussed next.

>>>>

Both \refcoco and \refcocop \cite{Yu2016} use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object. 
The matcher must click on the object she thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use location words, urging them to refer to the appearance of objects.
 % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories? How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ... and it nicely shows that natural names are much more variable than strict categories}
% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

Table \ref{tab:compare} shows that the multiple annotations ($2.84$\ on average) actually contain a considerable amount of variation in naming (almost 2 different names on average per object). However, the small number of annotations per object does not allow for a reliable assessment of speaker agreement.

RefCOCO has been used to model and examine the effect of context on referring expression generation in general \cite{Yu2016}, though this work did not look at object names specifically. 
A controlled analysis of the effect of context on choice in naming, as for instance in \cite{graf2016animal}, would require substantial further data annotation as not all objects of an image are annotated with REs and corresponding categories. Hence, so-called distractor objects  \cite{krahmer:2012} and their names cannot be analyzed systematically.
Also, while in \refcoco the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
Finally, the set of categories in MSCOCO included is quite small ($80$~COCO categories).
To sum up, \refcoco is suitable for generally modeling referring expressions in context for a restricted set of categories, but less appropriate for analyzing object naming at a large scale.

@@

While some existing resources do provide naming data for objects in context, they do not provide \textit{enough} data to systematically assess how variable or stable object naming really is. The RefCOCO data (and to some extent the Flickr30k data) suggests that for most objects there is more than one available name, but it is unclear which name most speakers would prefer or whether there is such a preferred name at all. 
The VG data, to the contrary, seems to indicate that the vast majority of objects should only be associated with a single name, but it is difficult to estimate to what extent this finding results from problems with annotation (partial linking).
This shows that to be able to analyze object naming in more detail, we simply need naming data from many subjects for the same objects. 
Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
These are the motivations for our dataset, ManyNames, and for building it on top of \vg, as discussed next.
